Atomify - a live LAMMPS visualizer

### 2017-04-12 ms.tex
SA will do features
Add newline at end of file
Moved to revtex4-1. May break on Mac?
Fix revtex and add features

\subsection{Script editor}
Atomify provides a lightweight script editor with syntax highlighting and line
numbers.
% TODO add built-in help and autocompletion to Atomify and mention here
Multiple files can be open at the same time and persist across working sessions.
The script can easily be restarted by clicking the button in the GUI or using
the default shortcut (Ctrl+R in Windows and Linux or Cmd+R in macOS).
Any changes made to the script are immediately visualized in the simulation.

\subsection{Visualization}
TODO: Color atoms based on property \\

\subsection{Dashboard}
TODO: Highlight groups/regions \\
TODO: Show/hide groups/regions \\
TODO: Rendering parameters \\
TODO: Atomify commands \\
TODO: Rendering parameters \\
TODO: Plot compute/variable/fix \\

@@

Atomify is built upon Qt.
All GUI is defined in QML whereas the backend of the program communicating with
LAMMPS is written in C++.
Simply put, Atomify runs an instance of a LAMMPS object enabling the user to
visualize the current state of LAMMPS and interact with LAMMPS while the
simulation is running.

>>>>

\subsection{Script editor}

Atomify provides a lightweight script editor with syntax highlighting and line
numbers.
% TODO add built-in help and autocompletion to Atomify and mention here
Multiple files can be open at the same time and persist across working sessions.
The script can easily be restarted by clicking the button in the GUI or using
the default shortcut (Ctrl+R in Windows and Linux or Cmd+R in macOS).
Any changes made to the script are immediately visualized in the simulation.

Certain Atomify-commands can be added to the comments of a regular LAMMPS script
to modify properties of the GUI.
For instance, the color and size of the atoms can be set based on the type by
the command \texttt{\#/atom}.
To set the color to white and radius to 2.0 for particle type 1,
the user can apply the command \texttt{\#/atom 1 2.0 \#ffffff}.
The initial camera position can also be set similarily.
For a full list of the available commands, see the Atomify documentation.

TODO: Add link to documentation

\subsection{Visualization}

Atomify provides live visualization of particles in a simulation in its 3D view.
The particles can be colored based on properties such as atom type,
velocity, and force.
The coloring scheme can be changed while the simulation is running by hovering
the mouse cursor over groups in the dashboard.
Light colors and strength can also be changed in the dashboard.
This will be described in further detail in the following section.

\subsection{Dashboard}

It is possible to organize particles in groups and regions in LAMMPS.
These are shown in the dashboard in Atomify, which also provides controls to
highlight or hide specific groups or regions.
To highlight a group or region, the user only needs to hover the name in the
dashboard.
The visibility icon can be clicked to hide a group or region.

Parameters for rendering, such as the light strength and color,
can be modified in the Rendering tab of the dashboard.
See the above section about the script editor for information about how to
modify the color of the particles.

In LAMMPS, computes are values calculated based on properties of the running
simulation.
Variables are user defined expressions which can be used to combine values in
calculations.
Once defined in a LAMMPS script, these can be plotted as a function of time in
Atomify.
This is done by clicking the name of the variable or compute in the simulation
tab.
We will explore plots in further detail in the following section.

TODO: fixes \\

@@

Atomify is built upon Qt.
All GUI is defined in QML whereas the backend of the program communicating with
LAMMPS is written in C++.
High-performance visualization is achieved by implementing billboards in Qt3D.
Simply put, Atomify runs an instance of a LAMMPS object enabling the user to
visualize the current state of LAMMPS and interact with LAMMPS while the
simulation is running.
